---
title: "Goodness of fit Tests"
author: "Arnau Garcia"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Goodness of fit tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library("GofCens")
```

# Goodness of fit tests for complete and right-censored data

In the `GofCens`package there are several goodness of fit methods. Let us illustrate how these methods work with different examples.

## Kolmogorov-Smirnov test

The Kolmogorov-Smirnov test is implemeted using a theoretical method and bootstrapping methods.

```{r}
set.seed(123)
survt <- round(rlnorm(300, 2, 1), 2)
censt <- round(rexp(300, 1 / 20), 2)
times <- pmin(survt, censt)
delta <- as.numeric(survt <= censt)
KScens(times, delta, distr = "lognormal")
```

We can print it in table format:

```{r}
set.seed(123)
print(KScens(times, delta, distr = "weibull"), outp = "table")
```

##  Cramér-von Mises test 

An example with the generated data is:

```{r}
set.seed(123)
CvMcens(times, delta, distr = "lognormal")
```

##  Anderson-Darling

An example printing with table format:

```{r}
set.seed(123)
print(ADcens(times, delta, distr = "lognormal", 
             params0 = list(location = 2, scale = 1.5)), outp = "table")
```

## Gofcens function

There is a function implemented computing the three p-values for the three previous tests simultaneously:

```{r}
set.seed(123)
gofcens(times, delta, distr = "lognormal")
```

## Chi-squared type test

Chi-squared type tests are also implemented by means of bootstrapping methods.

```{r}
set.seed(123)
chisqcens(times, delta, M = 8, distr = "lognormal")

```

