---
title: "Graphical Tools"
author: "Arnau Garcia"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Graphical Tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library("GofCens")
```

# Graphical tools for goodnes of fit

Several graphical tools are implemented to analyze the goodness of fit.

## Probability plot

The `probPlot()` function allows the user to assess graphically how well any of the distributions fit to a sample of complete or right-censored survival times.

```{r}
probPlot(times, delta, distr = "lognormal", prnt = FALSE, cex.lab = 1.3)
```

## Cumulative hazard plot

The `cumhazPlot()` function can be used to draw cumulative hazard plots for any of the distributions available.

```{r}
 cumhazPlot(times, delta, font.lab = 4, cex.lab = 1.3)
```

## Kaplan Meier plot

The `kmPlot()` function can be used to graphically compare the nonparametric estimation of the survival function of a complete or right-censored sample of survival times with the parametric estimations of the survival function under different parametric models.

```{r}
kmPlot(times, delta, colour = "blue", ggp = TRUE, prnt = FALSE)
```


